---
title: "Lab 00 - Hello IDS!"
author: "Jamie Zhan"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Lihan Gong", "Alma Brookes", "Neha Pillai", 
           "Catherine B", "Hoddy"),
  github_username = c("lgong25", "alma-bh", "nehapillai07", 
                      "catherineb012", "hodddy"), 
  colour = c("red", "blue", "pink", 
             "blue", "white"),
  hobby = c("reels", "reading", "badminton", 
            "golf", "guitar"),
  favourite_number = c(6, 6, 8, 3, 4)
  )



team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


## # A tibble: 5 × 5
##   name         github_username colour hobby     favourite_number
##   <chr>        <chr>           <chr>  <chr>                <dbl>
## 1 Lihan Gong   lgong25         red    reels                    6
## 2 Alma Brookes alma-bh         blue   reading                  6
## 3 Neha Pillai  nehapillai07    pink   badminton                8
## 4 Catherine B  catherineb012   blue   golf                     3
## 5 Hoddy        hodddy          white  guitar                   4

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Insert text here", 
          y = "Insert text here",
          title = "Insert text here")
```

*Remove this text (including the stars), and add your answer for Exercise 19 here.*

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

*Remove this text (including the stars) and add your answer for Exercise 20 here.*
