---
title: "Lab 00 - Hello IDS!"
author: "Jamie Zhan"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Lihan Gong", "Alma Brookes", "Neha Pillai", 
           "Catherine B", "Hoddy"),
  github_username = c("lgong25", "alma-bh", "nehapillai07", 
                      "catherineb012", "hodddy"), 
  colour = c("red", "blue", "pink", 
             "blue", "white"),
  hobby = c("reels", "reading", "badminton", 
            "golf", "guitar"),
  favourite_number = c(6, 6, 8, 3, 4)
  )



team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


## # A tibble: 5 × 5
##   name         github_username colour hobby     favourite_number
##   <chr>        <chr>           <chr>  <chr>                <dbl>
## 1 Lihan Gong   lgong25         red    reels                    6
## 2 Alma Brookes alma-bh         blue   reading                  6
## 3 Neha Pillai  nehapillai07    pink   badminton                8
## 4 Catherine B  catherineb012   blue   golf                     3
## 5 Hoddy        hodddy          white  guitar                   4

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Github Username", 
          y = "Favourite Number",
          title = "Lab 00")
```

The labs() function is for inserting labels onto plots.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

The data visualisation produced by this method would be worse at conveying information because the count increments by 0.25 which is unrealistic since hobbies can only be of integer values. This can be resolved by incrementing by 1 instead.
